Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-22 edubots_surveys.Rnw
Answer about insertion of citation #48

Several higher education chatbots' evaluation studies have been undertaken. For
instance, a recent evaluation review study presented by Smutny and Schreiberova
\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
Messenger with the focus to identify characteristics and quality metrics such as
language, subject matter and platform.  Whereas the study undertaken by
\cite{perez2020rediscovering} aimed to categorise educational chatbots according
to their purpose into service-oriented and teaching-oriented. The first category
includes those that provide service support such as the chatbot Ask Holly
\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
students' questions about enrolment and registration. Ask L. U.
\cite{LancasterUniversity_2019} answers students' frequently asked questions
about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
and Differ \cite{differ.chat} facilitate breaking the ice between new students
by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
proposed a generic chatbot for university students that is able to answer to
their frequently asked questions.  For some time, the University of Granada had
ELVIRA as a chatbot in its main web page \cite{MOREO20129}. Besides being able
to answer pre-established (frequent) questions, it did so from the website of
the University of Granada using an inset character, voiced by a real person, who
lip-synced the answers. The emphasis in the case of Elvira, however, was on the
authenticity of the synchronization more than in making the update of questions
and answers simpler, or more interactive, using actual messaging platforms.  In
most cases, using the inset search engine was able to give you more up-to-date
and accurate answers than the ones provided by ELVIRA, which had to be updated
by hand (and not too often).

>>>>

Several higher education chatbots' evaluation studies have been undertaken. For
instance, a recent evaluation review study presented by Smutny and Schreiberova
\cite{Smutny2020} examined 47 educational chatbots implemented in Facebook
Messenger with the focus to identify characteristics and quality metrics such as
language, subject matter and platform\textcolor{blue}{, whereas the study undertaken by Pérez and collaborators
\cite{perez2020rediscovering} aimed to categorise educational chatbots, according
to their, purpose into service-oriented and teaching-oriented}. The first category
includes those that provide service support such as the chatbot Ask Holly
\cite{meetholly} and Dina \cite{santoso2018dinus}; both chatbots respond to
students' questions about enrolment and registration. Ask L. U.
\cite{LancasterUniversity_2019} answers students' frequently asked questions
about timetables, grades, tutors and societies. LISA \cite{dibitonto2018chatbot}
and Differ \cite{differ.chat} facilitate breaking the ice between new students
by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
proposed a generic chatbot for university students that is able to answer to
their frequently asked questions.  For some time, the University of Granada had
ELVIRA as a chatbot in its main web page \cite{MOREO20129}. Besides being able
to answer pre-established (frequent) questions, it did so from the website of
the University of Granada using an inset character, voiced by a real person, who
lip-synced the answers. The emphasis in the case of Elvira, however, was on the
authenticity of the synchronization more than in making the update of questions
and answers simpler, or more interactive, using actual messaging platforms.  In
most cases, using the inset search engine was able to give you more up-to-date
and accurate answers than the ones provided by ELVIRA, which had to be updated
by hand (and not too often).
